Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-13 write-ups/PLDI/paper.tex
Add references to cooperative multitasking

>>>>

\HEComment{cooperative multitasking: OS: RISC OS, IBM CICS, Windows
  before 95, old MacOS, maybe Oberon? TRON?. In GPU context: some
  paper mention ``cooperative'' multitasking but they simply refer to
  the fact that kernels should not compute for too long in order to
  let other have access to it. Also, many prog languages implements
  variations of coroutines, We can see blocking channels of CSP (or
  Golang more recently) as yielding (sending a message is yielding
  computation to the process which receives it)}

Cooperative multitasking was offered in ancient operating systems
(e.g. Windows before the 95 edition) and is still used nowadays in
RISC OS for instance. In the context of GPU resources, cooperative
multitasking seems to refer to sizing kernels such that they do not
compute for too long in order to yield the whole GPU
regularly~\cite{adriaens2012case}. Our contribution present a much
more flexible cooperative multitasking, where the long-running
application is never totally stopped.

\HEComment{ RISC OS see :
\url{http://www.riscos.info/index.php/Preemptive_multitasking}
}

% ###
% Cooperative multitasking for GPU-accelerated grid systems

% http://onlinelibrary.wiley.com/doi/10.1002/cpe.1722/full

% @article {CPE:CPE1722,
% author = {Ino, Fumihiko and Ogita, Akihiro and Oita, Kentaro and Hagihara, Kenichi},
% title = {Cooperative multitasking for GPU-accelerated grid systems},
% journal = {Concurrency and Computation: Practice and Experience},
% volume = {24},
% number = {1},
% publisher = {John Wiley & Sons, Ltd},
% issn = {1532-0634},
% url = {http://dx.doi.org/10.1002/cpe.1722},
% doi = {10.1002/cpe.1722},
% pages = {96--107},
% keywords = {multitasking, GPU, CUDA, grid computing},
% year = {2012},
% }

% Not super interesting: they just divide blocking computation in
% smaller independent kernels, and fires them at regular intervals to
% let the system be responsive.
